---
title: "Pattern of Smoking across different Sub-population"
author: "Opeyemi Amodu"
date: "11/2/2020"
output: pdf_document
---

```{r setup, include=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE, warning = FALSE, mesage=FALSE)
library(tidyverse)
library(gridExtra)
library(survey)
library(knitr)
```


To produce this report, The "tidyverse", "survey", "gridExtra", "knitr" packages should be installed. Please run the following code in R or Rstudio;

```{r, echo = TRUE, warning = FALSE, results = "hide", message = FALSE}
installed_pkgs <- row.names(installed.packages())
pkgs <- c("dplyr", "gridExtra", "survey", "knitr")

for(p in pkgs){
if(!(p %in% installed_pkgs)){
install.packages(p, repos = "http://cran.us.r-project.org")
 }
 }
```

```{r}
nhis19 <- read.csv("final_data_2019_clean.csv")
```

### Building the survey design using survey weights

I created the survey design as specified by the summary documentation provided by the National Health Survey Interview Statistics. This document can be found at the [NHIS website](https://www.cdc.gov/nchs/nhis/2019nhis.htm). 

```{r, echo = TRUE, results = "hide"}
nhis19_design <- svydesign(id=~PPSU, strata= ~PSTRAT, nest = TRUE,
                              weights = ~WTFA_A, data = nhis19)
summary(nhis19_design)
```

# Descriptive Statistics

<!--
The prev_tab_function below calculates total prevalence by type of product in percentage
- the object is the object is the object created using the survey design
- the col_name is the type of smoke product 
_ label is the name to give the type of product eg. Cigarette, Smokeless Tobacco etc.
- I use the function for each type of product and then binded the table to form one big table
-->

```{r}
prev_tab_function <- function(object, col_name, label){
  df <- object %>%
  as.data.frame()%>%
  spread({{col_name}}, Freq)%>%
  mutate(`Prevalence (%)` = round((Yes/(Yes + No))*100, 1))
  
  df$`Type of Product` <- label
  
  df <- df %>%
    select(`Type of Product`, `Prevalence (%)`)
  
  df
}

```

## General Cigarette Smoking
```{r}
cig_smoking <- svytable(~SMKCIGST_A,
                   design = nhis19_design)

ecig_smoking <- svytable(~SMKECIGST_A, 
                   design = nhis19_design)

cigar_smoking <- svytable(~CIGARST_A, 
                   design = nhis19_design)

pipe_smoking<- svytable(~PIPEST_A,
                        design = nhis19_design)

smkles_smoking <- svytable(~SMOKELSST_A,
                          design =nhis19_design)
cig_use <- prev_tab_function(cig_smoking, SMKCIGST_A, "Cigarette")
ecig_use <- prev_tab_function(ecig_smoking, SMKECIGST_A, "Smokeless Tobacco")
cigar_use <- prev_tab_function(cigar_smoking, CIGARST_A, "Cigar")
pipe_use <- prev_tab_function(pipe_smoking, PIPEST_A, "Pipe")
smkles_use <- prev_tab_function(smkles_smoking, SMOKELSST_A, "Smokeless tobacco")

general_use <- bind_rows(cig_use, ecig_use, cigar_use, pipe_use, smkles_use)
kable(general_use, caption = "Smoking Prevalence in the United States")
```

<!--
the df_function calculates smoking prevalence by type of product and socio-economic/socio-demographic variable 
of interest. For example Smokeless tobacco by age or Cigarette by sex
- object is the object created using the survey design
- col_name_1 represents the Socio-economic/socio-demographic variable of interest
- col_name_2 represents the type of smoking product
-->
```{r, function for dataframes}
df_function <- function(object, col_name_1, col_name_2){
  df <- object %>% 
    as.data.frame()%>%
    group_by({{col_name_1}})%>%
    gather({{col_name_2}}, key = "Type of Product", value = "Smoking Status")%>%
    spread(`Smoking Status`, Freq)%>%
    mutate(`Prevalence (%)` = round((Yes/(Yes + No))*100, 1))%>%
    select(`-`={{col_name_1}}, `Type of Product`, `Prevalence (%)`)
  
  df$`Type of Product` <- ifelse(df$`Type of Product` == "SMKCIGST_A", "Cigarette", 
                                 ifelse(df$`Type of Product` == "SMKECIGST_A", "E-cigarette",
                                        ifelse(df$`Type of Product` == "CIGARST_A", "Cigar",
                                               ifelse(df$`Type of Product` == "PIPEST_A", "Pipe",
                                                      ifelse(df$`Type of Product` == "SMOKELSST_A", "Smokeless tobacco", "")))))
  
  
  df
}

```

\newpage
## Smoking by Age
```{r}
#cigarette smoking objects by age 
cig_by_age <- svytable(~SMKCIGST_A + binned_age,
                   design = nhis19_design)



ecig_by_age <- svytable(~SMKECIGST_A + binned_age,
                        design = nhis19_design)


cigar_by_age <- svytable(~CIGARST_A + binned_age,
                         design = nhis19_design)


pipe_by_age <- svytable(~PIPEST_A + binned_age,
                        design = nhis19_design)


smkles_by_age <- svytable(~SMOKELSST_A + binned_age,
                          design =nhis19_design)
```


```{r}
#Cigarette by age
cig_by_ageDF <- df_function(cig_by_age, binned_age, SMKCIGST_A)

#e-cigarette by age
ecig_by_ageDF <- df_function(ecig_by_age, binned_age, SMKECIGST_A)

#cigar by age
cigar_by_ageDF <- df_function(cigar_by_age, binned_age, CIGARST_A)

# pipe smoke by age
pipe_by_ageDF <- df_function(pipe_by_age, binned_age, PIPEST_A)

# smokeless tobacco by age
smkles_by_ageDF <- df_function(smkles_by_age, binned_age, SMOKELSST_A)

# Combining all into one table 
smoking_by_age <- bind_rows(cig_by_ageDF, ecig_by_ageDF, cigar_by_ageDF, pipe_by_ageDF, smkles_by_ageDF)
kable(smoking_by_age, caption = "Table Showing Prevalence of Smoking by Age and Type of Product")

```

## Smoking Prevalence by Gender
```{r}
#cigarette smoking objects by sex
cig_by_sex <- svytable(~SMKCIGST_A + SEX_A ,
                   design = nhis19_design)

ecig_by_sex <- svytable(~SMKECIGST_A + SEX_A,
                        design = nhis19_design)

cigar_by_sex <- svytable(~CIGARST_A +SEX_A,
                         design = nhis19_design)

pipe_by_sex <- svytable(~PIPEST_A + SEX_A,
                        design = nhis19_design)

smkles_by_sex <- svytable(~SMOKELSST_A + SEX_A,
                          design =nhis19_design)
```

```{r}
#cigarette
cig_by_sexDF <- df_function(cig_by_sex, SEX_A, SMKCIGST_A)

#e-cigarette
ecig_by_sexDF <- df_function(ecig_by_sex, SEX_A, SMKECIGST_A)

#cigar
cigar_by_sexDF <- df_function(cigar_by_sex, SEX_A, CIGARST_A)

#pipe
pipe_by_sexDF <- df_function(pipe_by_sex, SEX_A, PIPEST_A)

#smokeless tobacco
smkles_by_sexDF <- df_function(smkles_by_sex, SEX_A, SMOKELSST_A)

#Combining all into one table 
smoking_by_sex <- bind_rows(cig_by_sexDF, ecig_by_sexDF, cigar_by_sexDF, pipe_by_sexDF, smkles_by_sexDF)
kable(smoking_by_sex, caption = "Table Showing Prevalence of Smoking by Sex and Type of Product")
```


## Smoking by Race/Ethinicity
```{r}
cig_by_race <- svytable(~RACEALLP_A + SMKCIGST_A,
                   design = nhis19_design)
#e-cig use by race
ecig_by_race <- svytable(~RACEALLP_A +SMKECIGST_A,
                        design = nhis19_design)

#cigar use by age and by race
cigar_by_race <- svytable(~RACEALLP_A+CIGARST_A,
                         design = nhis19_design)

#pipe use by age and by race
pipe_by_race <- svytable(~RACEALLP_A +PIPEST_A,
                        design = nhis19_design)

#smokeless tobacco use by race
smkles_by_race <- svytable(~RACEALLP_A+SMOKELSST_A,
                          design =nhis19_design)

```

```{r}
#cigarette
cig_by_raceDF <- df_function(cig_by_race, RACEALLP_A, SMKCIGST_A)
# cig_by_raceDF <- cig_by_race %>% 
#   as.data.frame()%>%
#   group_by(RACEALLP_A)%>%
#   gather(`SMKCIGST_A`, key = "Type of Smoke", value = "Smoking Status")%>%
#   spread(`Smoking Status`, Freq)%>%
#   mutate(Prevalence = (Yes/(Yes + No))*100)
# cig_by_raceDF$`Type of Smoke` <- ifelse(cig_by_raceDF$`Type of Smoke` == "SMKCIGST_A", "Cigarette", "")

#ecigarette
ecig_by_raceDF <- df_function(ecig_by_race, RACEALLP_A, SMKECIGST_A)
# ecig_by_raceDF <- ecig_by_race %>% 
#   as.data.frame()%>%
#   group_by(RACEALLP_A)%>%
#   gather(`SMKECIGST_A`, key = "Type of Smoke", value = "Smoking Status")%>%
#   spread(`Smoking Status`, Freq)%>%
#   mutate(Prevalence = (Yes/(Yes + No))*100)
# ecig_by_raceDF$`Type of Smoke` <- ifelse(ecig_by_raceDF$`Type of Smoke` == "SMKECIGST_A", "E-Cigarette", "")

#cigar
cigar_by_raceDF <- df_function(cigar_by_race, RACEALLP_A, CIGARST_A)

#pipe
pipe_by_raceDF <- df_function(pipe_by_race, RACEALLP_A, PIPEST_A)

#smokeless tobacco
smkles_by_raceDF <- df_function(smkles_by_race, RACEALLP_A, SMOKELSST_A)

smoking_by_race <- rbind(cig_by_raceDF, ecig_by_raceDF, cigar_by_raceDF, pipe_by_raceDF, smkles_by_raceDF)
kable(smoking_by_race, caption ="Smoking Prevalence by Race and type of Smoke")


```


## Smoking by Education

```{r}
cig_by_education <- svytable(~binned_EDUC + SMKCIGST_A,
                   design = nhis19_design)

#e-cig use by education
ecig_by_education <- svytable(~binned_EDUC +SMKECIGST_A,
                        design = nhis19_design)

#cigar use by age and by education
cigar_by_education <- svytable(~binned_EDUC+CIGARST_A,
                         design = nhis19_design)

#pipe use by age and by education
pipe_by_education <- svytable(~binned_EDUC +PIPEST_A,
                        design = nhis19_design)

#smokeless tobacco use by education
smkles_by_education <- svytable(~binned_EDUC+SMOKELSST_A,
                          design =nhis19_design)
```

```{r}
#cigarette
cig_by_educDF <- df_function(cig_by_education, binned_EDUC, SMKCIGST_A)

#ecigarette
ecig_by_educDF <- df_function(ecig_by_education, binned_EDUC, SMKECIGST_A)

#cigar
cigar_by_educDF <- df_function(cigar_by_education, binned_EDUC, CIGARST_A)

#pipe
pipe_by_educDF <- df_function(pipe_by_education, binned_EDUC, PIPEST_A)

#smokeless tobacco
smkles_by_educDF <-df_function(smkles_by_education, binned_EDUC, SMOKELSST_A)

smoking_by_educ <- rbind(cig_by_educDF, ecig_by_educDF, cigar_by_educDF, pipe_by_educDF,smkles_by_educDF)
kable(smoking_by_educ, caption ="Smoking Prevalence by Education and type of Smoke")


```

## Smoking by Income Relative to Federal Poverty Level

```{r}
cig_by_pov <- svytable(~binned_RATCAT + SMKCIGST_A,
                   design = nhis19_design)

#e-cig use by poverty level
ecig_by_pov <- svytable(~binned_RATCAT +SMKECIGST_A,
                        design = nhis19_design)

#cigar use by poverty level
cigar_by_pov <- svytable(~binned_RATCAT+CIGARST_A,
                         design = nhis19_design)

#pipe use by poverty level
pipe_by_pov <- svytable(~binned_RATCAT +PIPEST_A,
                        design = nhis19_design)

#smokeless tobacco use by poverty level
smkles_by_pov <- svytable(~binned_RATCAT+SMOKELSST_A,
                          design =nhis19_design)
```

```{r}
#cigarette
cig_by_povDF <- df_function(cig_by_pov, binned_RATCAT, SMKCIGST_A)

#e-cigarette
ecig_by_povDF <- df_function(ecig_by_pov, binned_RATCAT, SMKECIGST_A)

#cigar
cigar_by_povDF <- df_function(cigar_by_pov, binned_RATCAT, CIGARST_A)

#pipe
pipe_by_povDF <- df_function(pipe_by_pov, binned_RATCAT, PIPEST_A)

#smokeless tobacco
smkles_by_povDF <- df_function(smkles_by_pov, binned_RATCAT, SMOKELSST_A)

#combining all 
smoking_by_pov <- rbind(cig_by_povDF, ecig_by_povDF, cigar_by_povDF, pipe_by_povDF,smkles_by_povDF)
kable(smoking_by_pov, caption ="Smoking Prevalence by Ratio of Family Income to Federal Poverty Level")

```



## Smoking by Sexual Orientation 

```{r}
cig_by_sexorient <- svytable(~ORIENT_A + SMKCIGST_A,
                   design = nhis19_design)

#e-cig use by poverty level
ecig_by_sexorient <- svytable(~ORIENT_A +SMKECIGST_A,
                        design = nhis19_design)

#cigar use by poverty level
cigar_by_sexorient <- svytable(~ORIENT_A+CIGARST_A,
                         design = nhis19_design)

#pipe use by poverty level
pipe_by_sexorient <- svytable(~ORIENT_A+PIPEST_A,
                        design = nhis19_design)

#smokeless tobacco use by poverty level
smkles_by_sexorient <- svytable(~ORIENT_A+SMOKELSST_A,
                          design =nhis19_design)
```

```{r}
# cigarette
cig_by_sexorientDF <- df_function(cig_by_sexorient, ORIENT_A, SMKCIGST_A)

# e-cigarette
ecig_by_sexorientDF <- df_function(ecig_by_sexorient, ORIENT_A, SMKECIGST_A)

# cigar
cigar_by_sexorientDF <- df_function(cigar_by_sexorient, ORIENT_A, CIGARST_A)

# pipe
pipe_by_sexorientDF <- df_function(pipe_by_sexorient, ORIENT_A, PIPEST_A)

# smokeless tobacco
smkles_by_sexorientDF <- df_function(smkles_by_sexorient, ORIENT_A, SMOKELSST_A)

# Combining all 
smoking_by_sexorient <- rbind(cig_by_sexorientDF, ecig_by_sexorientDF, cigar_by_sexorientDF, pipe_by_sexorientDF,smkles_by_sexorientDF)
kable(smoking_by_sexorient, caption ="Smoking Prevalence by Sexual Orientation")

```

## Smoking by Mental Health status
<!--
I created a separate mental health dataframe function because mental health relies on 2 variables;
depression and anxiety
-->

```{r}
mental_health_df_function <- function(object, col_name_1, col_name_2){
  object %>% 
  as.data.frame()%>%
  filter({{col_name_1}} == "Yes")%>%
  gather({{col_name_1}}, key = "Mental Health", value = "Mental_hlth_status")%>%
  gather({{col_name_2}}, key = "Type of Product", value = "Smoking Status")%>%
  spread(`Smoking Status`, Freq)
  
}

#creating depression objects
cig_by_depress <- svytable(~DEPEV_A + SMKCIGST_A,
                           design = nhis19_design)

ecig_by_depress <- svytable(~DEPEV_A + SMKECIGST_A,
                           design = nhis19_design)

cigar_by_depress <- svytable(~DEPEV_A + CIGARST_A,
                           design = nhis19_design)

pipe_by_depress <- svytable(~DEPEV_A + PIPEST_A,
                           design = nhis19_design)

smkles_by_depress <- svytable(~DEPEV_A + SMOKELSST_A,
                           design = nhis19_design)

#creating anxiety objects
cig_by_anxiety <- svytable(~ANXEV_A + SMKCIGST_A,
                           design = nhis19_design)

ecig_by_anxiety <- svytable(~ANXEV_A + SMKECIGST_A,
                           design = nhis19_design)

cigar_by_anxiety <- svytable(~ANXEV_A + CIGARST_A,
                           design = nhis19_design)

pipe_by_anxiety <- svytable(~ANXEV_A + PIPEST_A,
                           design = nhis19_design)

smkles_by_anxiety <- svytable(~ANXEV_A + SMOKELSST_A,
                           design = nhis19_design)

#creating data frames for Dementia
cig_by_dementia <- svytable(~DEMENEV_A + SMKCIGST_A,
                           design = nhis19_design)



cigar_by_dementia <- svytable(~DEMENEV_A + CIGARST_A,
                           design = nhis19_design)

ecig_by_dementia <- svytable(~DEMENEV_A + SMKECIGST_A,
                           design = nhis19_design)

pipe_by_dementia <- svytable(~DEMENEV_A + PIPEST_A,
                           design = nhis19_design)

smkles_by_dementia <- svytable(~DEMENEV_A+ SMOKELSST_A,
                           design = nhis19_design)


#creating depression data frames
cig_by_depressDF <- mental_health_df_function(cig_by_depress, DEPEV_A, SMKCIGST_A)


ecig_by_depressDF <- mental_health_df_function(ecig_by_depress, DEPEV_A, SMKECIGST_A)


cigar_by_depressDF <- mental_health_df_function(cigar_by_depress, DEPEV_A, CIGARST_A)


pipe_by_depressDF <- mental_health_df_function(pipe_by_depress, DEPEV_A, PIPEST_A)


smkles_by_depressDF <- mental_health_df_function(smkles_by_depress, DEPEV_A, SMOKELSST_A)


#creating anxiety data frames
cig_by_anxietyDF <- mental_health_df_function(cig_by_anxiety, ANXEV_A, SMKCIGST_A)

ecig_by_anxietyDF <- mental_health_df_function(ecig_by_anxiety, ANXEV_A, SMKECIGST_A) 


cigar_by_anxietyDF <- mental_health_df_function(cigar_by_anxiety, ANXEV_A, CIGARST_A)


pipe_by_anxietyDF <- mental_health_df_function(pipe_by_anxiety, ANXEV_A, PIPEST_A)


smkles_by_anxietyDF <- mental_health_df_function(smkles_by_anxiety, ANXEV_A, SMOKELSST_A)


#creating dementia data frames

cig_by_dementiaDF <- mental_health_df_function(cig_by_dementia, DEMENEV_A, SMKCIGST_A)

ecig_by_dementiaDF <- mental_health_df_function(ecig_by_dementia, DEMENEV_A, SMKECIGST_A) 

cigar_by_dementiaDF <- mental_health_df_function(cigar_by_dementia, DEMENEV_A, CIGARST_A)

pipe_by_dementiaDF <- mental_health_df_function(pipe_by_dementia, DEMENEV_A, PIPEST_A)

smkles_by_dementiaDF <- mental_health_df_function(smkles_by_dementia, DEMENEV_A, SMOKELSST_A)

smoking_by_mentalhlth <- bind_rows(cig_by_depressDF, cig_by_anxietyDF, cig_by_dementiaDF,
                                   ecig_by_depressDF, ecig_by_anxietyDF, ecig_by_dementiaDF,
                                   pipe_by_depressDF, pipe_by_anxietyDF, pipe_by_dementiaDF,
                                   cigar_by_depressDF, cigar_by_anxietyDF, cigar_by_dementiaDF,
                                   smkles_by_depressDF, smkles_by_anxietyDF, smkles_by_dementiaDF)

smoking_by_mentalhlth <- select(smoking_by_mentalhlth, -Mental_hlth_status)


smoking_by_mentalhlth$`Type of Product` <- ifelse(smoking_by_mentalhlth$`Type of Product` == "SMKCIGST_A", "Cigarette",
                                         ifelse(smoking_by_mentalhlth$`Type of Product` == "SMKECIGST_A", "E-cigarette",
                                         ifelse(smoking_by_mentalhlth$`Type of Product` == "PIPEST_A", "Pipe",
                                         ifelse(smoking_by_mentalhlth$`Type of Product` == "CIGARST_A", "Cigar",
                                         ifelse(smoking_by_mentalhlth$`Type of Product` == "SMOKELSST_A", "Smokeless Tobacco", "")))))

smoking_by_mentalhlth$`Mental Health` <- ifelse(smoking_by_mentalhlth$`Mental Health` == "DEPEV_A", "Depression",
                                         ifelse(smoking_by_mentalhlth$`Mental Health` == "ANXEV_A", "Anxiety",
                                         ifelse(smoking_by_mentalhlth$`Mental Health` == "DEMENEV_A", "Dementia", "")))

smoking_by_mentalhlth <- mutate(smoking_by_mentalhlth, `Prevalence (%)` = round((Yes/(Yes + No))*100, 1))
smoking_by_mentalhlth  <- smoking_by_mentalhlth %>%
  select(`Mental Health`,`Type of Product`, `Prevalence (%)`)
kable(smoking_by_mentalhlth, caption = "Prevalence of Smoking among people with Mental health Problems")
```

## Dual Smoking Status (Cigarette and other Products)

```{r}
cig_by_agedual <- svytable(~binned_age + SMKCIGST_A,
                   design = nhis19_design)
cig_by_agedual <- cig_by_agedual%>%
  as.data.frame()%>%
  spread(`SMKCIGST_A`, Freq)%>%
  mutate(`Prevalence of cigarette` = round((Yes/(Yes + No))*100, 1))%>%
  select(binned_age, `Prevalence of cigarette`)


ecig_by_agedual <- svytable(~binned_age + SMKECIGST_A,
                        design = nhis19_design)
ecig_by_agedual <- ecig_by_agedual%>%
  as.data.frame()%>%
  spread(`SMKECIGST_A`, Freq)%>%
  mutate(`Prevalence of E-cigarette` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Prevalence of E-cigarette`)
  


cigar_by_agedual <- svytable(~binned_age +CIGARST_A,
                         design = nhis19_design)
cigar_by_agedual <- cigar_by_agedual%>%
  as.data.frame()%>%
  spread(`CIGARST_A`, Freq)%>%
  mutate(`Prevalence of Cigar` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Prevalence of Cigar`)


pipe_by_agedual <- svytable(~binned_age + PIPEST_A,
                        design = nhis19_design)
pipe_by_agedual <- pipe_by_agedual%>%
  as.data.frame()%>%
  spread(`PIPEST_A`, Freq)%>%
  mutate(`Prevalence of Pipe` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Prevalence of Pipe`)
  

smkles_by_agedual <- svytable(~binned_age + SMOKELSST_A,
                          design =nhis19_design)
smkles_by_agedual <- smkles_by_agedual%>%
  as.data.frame()%>%
  spread(`SMOKELSST_A`, Freq)%>%
  mutate(`Prevalence of Smokeless Tobacco` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Prevalence of Smokeless Tobacco`)
  

cig_ecig_by_agedual <- svytable(~binned_age + cig_ecig,
                              design = nhis19_design)
cig_ecig_by_agedual <- cig_ecig_by_agedual%>%
   as.data.frame()%>%
  spread(cig_ecig, Freq)%>%
  mutate(`Dual prevalence cigaratte and e-cig` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Dual prevalence cigaratte and e-cig`)
  

cig_pipe_by_agedual <- svytable(~binned_age + cig_pipe,
                              design = nhis19_design)
cig_pipe_by_agedual <- cig_pipe_by_agedual%>%
  as.data.frame()%>%
  spread(`cig_pipe`, Freq)%>%
  mutate(`Dual prevalence cigaratte and pipe` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Dual prevalence cigaratte and pipe`)

cig_cigar_by_agedual <- svytable(~binned_age + cig_cigar,
                               design = nhis19_design)
cig_cigar_by_agedual <- cig_cigar_by_agedual%>%
  as.data.frame()%>%
  spread(`cig_cigar`, Freq)%>%
  mutate(`Dual prevalence cigaratte and cigar` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Dual prevalence cigaratte and cigar`)
  

cig_smkles_by_agedual <- svytable(~binned_age + cig_smkles,
                                design = nhis19_design)
cig_smkles_by_agedual <- cig_smkles_by_agedual%>%
  as.data.frame()%>%
  spread(`cig_smkles`, Freq)%>%
  mutate(`Dual prevalence cigaratte and smokeless tobacco` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Dual prevalence cigaratte and smokeless tobacco`)
  
cig_ecig_table <- bind_cols(cig_by_agedual, ecig_by_agedual, cig_ecig_by_agedual)
kable(cig_ecig_table, caption = "Dual Prevalence of Cigarette and E-cigarette")

cig_cigar_table <- bind_cols(cig_by_agedual, cigar_by_agedual, cig_cigar_by_agedual)
kable(cig_cigar_table, caption = "Dual Prevalence of Cigarette and Cigar")

cig_pipe_table <- bind_cols(cig_by_agedual, pipe_by_agedual, cig_pipe_by_agedual)
kable(cig_pipe_table, caption = "Dual Prevalence of Cigarette and Pipe")

cig_smkles_table <- bind_cols(cig_by_agedual, smkles_by_agedual, cig_smkles_by_agedual)
kable(cig_smkles_table, caption = "Dual Prevalence of Cigarette and Smokeless Tobacco")
```


