---
title: "Pattern of Smoking Prevalence across different Sub-population in the United States for year 2018"
date: "11/13/2020"
output: pdf_document
---

```{r setup, include=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, warning = FALSE)
library(tidyverse)
library(gridExtra)
library(survey)
library(knitr)
```

```{r}
nhis18 <- read.csv("final_data_2018_clean.csv")
```

## Building the survey design using survey weights


```{r, echo = TRUE, results = "hide"}
nhis18_design <- svydesign(id=~PPSU, strata= ~PSTRAT, nest = TRUE,
                              weights = ~WTFA_SA, data = nhis18)
summary(nhis18_design)
```


```{r}
cig_smoking <- svytable(~SMKCIGST_A,
                   design = nhis18_design)

#cigarette smoking by age and sex
cig_by_sex <- svytable(~SMKCIGST_A + SEX,
                   design = nhis18_design)

ecig_by_sex <- svytable(~SMKECIGST_A + SEX,
                        design = nhis18_design)

cigar_by_sex <- svytable(~CIGARST_A +SEX,
                         design = nhis18_design)

pipe_by_sex <- svytable(~PIPEST_A + SEX,
                        design = nhis18_design)

smkles_by_sex <- svytable(~SMOKELSST_A + SEX,
                          design =nhis18_design)

cig_by_age <- svytable(~SMKCIGST_A + binned_age,
                   design = nhis18_design)



ecig_by_age <- svytable(~SMKECIGST_A + binned_age,
                        design = nhis18_design)



cigar_by_age <- svytable(~CIGARST_A + binned_age,
                         design = nhis18_design)



pipe_by_age <- svytable(~PIPEST_A + binned_age,
                        design = nhis18_design)


smkles_by_age <- svytable(~SMOKELSST_A + binned_age,
                          design =nhis18_design)
```

```{r, function for dataframes}
df_function <- function(object, col_name_1, col_name_2){
  object %>% 
  as.data.frame()%>%
  group_by({{col_name_1}})%>%
  gather({{col_name_2}}, key = "Type of Smoke", value = "Smoking Status")%>%
  spread(`Smoking Status`, Freq)%>%
  mutate(`Prevalence (%)` = round((Yes/(Yes + No))*100, 1))
  
}

```
### Smoking Prevalence by Age

```{r}
#
cig_by_ageDF <- df_function(cig_by_age, binned_age, SMKCIGST_A)
cig_by_ageDF$`Type of Smoke` <- ifelse(cig_by_ageDF$`Type of Smoke` == "SMKCIGST_A", "Cigarette")

ecig_by_ageDF <- df_function(ecig_by_age, binned_age, SMKECIGST_A)
ecig_by_ageDF$`Type of Smoke` <- ifelse(ecig_by_ageDF$`Type of Smoke` == "SMKECIGST_A", "E-cigarette", "")


#
cigar_by_ageDF <- df_function(cigar_by_age, binned_age, CIGARST_A)
cigar_by_ageDF$`Type of Smoke` <- ifelse(cigar_by_ageDF$`Type of Smoke` == "CIGARST_A", "Cigar", "")

#
pipe_by_ageDF <- df_function(pipe_by_age, binned_age, PIPEST_A)
pipe_by_ageDF$`Type of Smoke` <- ifelse(pipe_by_ageDF$`Type of Smoke` == "PIPEST_A", "Pipe", "")

smkles_by_ageDF <- df_function(smkles_by_age, binned_age, SMOKELSST_A)
smkles_by_ageDF$`Type of Smoke` <- ifelse(smkles_by_ageDF$`Type of Smoke` == "SMOKELSST_A", "Smokeless Tobacco", "")

smoking_by_age <- bind_rows(cig_by_ageDF, ecig_by_ageDF, cigar_by_ageDF, pipe_by_ageDF, smkles_by_ageDF)
kable(smoking_by_age, caption = "Table Showing Smoking by Age and Type of Product")

```
\newpage
### Smoking Prevalence by Gender

```{r}
cig_by_sexDF <- df_function(cig_by_sex, SEX, SMKCIGST_A)
cig_by_sexDF$`Type of Smoke` <- ifelse(cig_by_sexDF$`Type of Smoke` == "SMKCIGST_A", "Cigarette", "")

#
ecig_by_sexDF <- df_function(ecig_by_sex, SEX, SMKECIGST_A)
ecig_by_sexDF$`Type of Smoke` <- ifelse(ecig_by_sexDF$`Type of Smoke` == "SMKECIGST_A", "E-cigarette", "")

#
cigar_by_sexDF <- df_function(cigar_by_sex, SEX, CIGARST_A)
cigar_by_sexDF$`Type of Smoke` <- ifelse(cigar_by_sexDF$`Type of Smoke` == "CIGARST_A", "Cigar", "")

#
pipe_by_sexDF <- df_function(pipe_by_sex, SEX, PIPEST_A)
pipe_by_sexDF$`Type of Smoke` <- ifelse(pipe_by_sexDF$`Type of Smoke` == "PIPEST_A", "Pipe", "")

#
smkles_by_sexDF <- df_function(smkles_by_sex, SEX, SMOKELSST_A)
smkles_by_sexDF$`Type of Smoke` <- ifelse(smkles_by_sexDF$`Type of Smoke` == "SMOKELSST_A", "Smokeless Tobacco", "")

smoking_by_sex <- bind_rows(cig_by_sexDF, ecig_by_sexDF, cigar_by_sexDF, pipe_by_sexDF, smkles_by_sexDF)
kable(smoking_by_sex, caption = "Table Showing Prevalence of Smoking by Sex and Type of Product")

```

### Smoking Prevalence by Race/Ethnicity

```{r}
cig_by_race <- svytable(~RACERPI2 + SMKCIGST_A,
                   design = nhis18_design)
#e-cig use by race
ecig_by_race <- svytable(~RACERPI2 + SMKECIGST_A,
                        design = nhis18_design)

#cigar use by age and by race
cigar_by_race <- svytable(~RACERPI2 + CIGARST_A,
                         design = nhis18_design)

#pipe use by age and by race
pipe_by_race <- svytable(~RACERPI2 +PIPEST_A,
                        design = nhis18_design)

#smokeless tobacco use by race
smkles_by_race <- svytable(~RACERPI2 + SMOKELSST_A,
                          design =nhis18_design)
```

```{r}
cig_by_raceDF <- df_function(cig_by_race, RACERPI2, SMKCIGST_A)
cig_by_raceDF$`Type of Smoke` <- ifelse(cig_by_raceDF$`Type of Smoke` == "SMKCIGST_A", "Cigarette", "")

#
ecig_by_raceDF <- df_function(ecig_by_race, RACERPI2, SMKECIGST_A)
ecig_by_raceDF$`Type of Smoke` <- ifelse(ecig_by_raceDF$`Type of Smoke` == "SMKECIGST_A", "E-Cigarette", "")

#
cigar_by_raceDF <- df_function(cigar_by_race, RACERPI2, CIGARST_A)
cigar_by_raceDF$`Type of Smoke` <- ifelse(cigar_by_raceDF$`Type of Smoke` == "CIGARST_A", "Cigar", "")

#
pipe_by_raceDF <- df_function(pipe_by_race, RACERPI2, PIPEST_A)
pipe_by_raceDF$`Type of Smoke` <- ifelse(pipe_by_raceDF$`Type of Smoke` == "PIPEST_A", "Pipe", "")

#
smkles_by_raceDF <- df_function(smkles_by_race, RACERPI2, SMOKELSST_A)
smkles_by_raceDF$`Type of Smoke` <- ifelse(smkles_by_raceDF$`Type of Smoke` == "SMOKELSST_A", "Smokeless Tobacco", "")

smoking_by_race <- rbind(cig_by_raceDF, ecig_by_raceDF, cigar_by_raceDF, pipe_by_raceDF, smkles_by_raceDF)
kable(smoking_by_race, caption ="Smoking Prevalence by Race and type of Smoke")
```
\newpage
### Smoking Prevalence by Education

```{r}
cig_by_education <- svytable(~EDUC1 + SMKCIGST_A,
                   design = nhis18_design)

#e-cig use by education
ecig_by_education <- svytable(~EDUC1 +SMKECIGST_A,
                        design = nhis18_design)

#cigar use by age and by education
cigar_by_education <- svytable(~EDUC1+CIGARST_A,
                         design = nhis18_design)

#pipe use by age and by education
pipe_by_education <- svytable(~EDUC1 +PIPEST_A,
                        design = nhis18_design)

#smokeless tobacco use by education
smkles_by_education <- svytable(~EDUC1+SMOKELSST_A,
                          design =nhis18_design)
```

```{r}
cig_by_educDF <- df_function(cig_by_education, EDUC1, SMKCIGST_A)
cig_by_educDF$`Type of Smoke` <- ifelse(cig_by_educDF$`Type of Smoke` == "SMKCIGST_A", "Cigarette", "")

#
ecig_by_educDF <- df_function(ecig_by_education, EDUC1, SMKECIGST_A)
ecig_by_educDF$`Type of Smoke` <- ifelse(ecig_by_educDF$`Type of Smoke` == "SMKECIGST_A", "E-Cigarette", "")

#
cigar_by_educDF <- df_function(cigar_by_education, EDUC1, CIGARST_A)
cigar_by_educDF$`Type of Smoke` <- ifelse(cigar_by_educDF$`Type of Smoke` == "CIGARST_A", "Cigar", "")

#
pipe_by_educDF <- df_function(pipe_by_education, EDUC1, PIPEST_A)
pipe_by_educDF$`Type of Smoke` <- ifelse(pipe_by_educDF$`Type of Smoke` == "PIPEST_A", "Pipe", "")

#
smkles_by_educDF <-df_function(smkles_by_education, EDUC1, SMOKELSST_A)
smkles_by_educDF$`Type of Smoke` <- ifelse(smkles_by_educDF$`Type of Smoke` == "SMOKELSST_A", "Smokeless Tobacco", "")

smoking_by_educ <- rbind(cig_by_educDF, ecig_by_educDF, cigar_by_educDF, pipe_by_educDF,smkles_by_educDF)
kable(smoking_by_educ, caption ="Smoking Prevalence by Education and type of Smoke")
```
\newpage
### Smoking Prevalence by Income Relative to Federal Poverty Level

```{r}
cig_by_pov <- svytable(~binned_RATCAT + SMKCIGST_A,
                   design = nhis18_design)

#e-cig use by poverty level
ecig_by_pov <- svytable(~binned_RATCAT +SMKECIGST_A,
                        design = nhis18_design)

#cigar use by poverty level
cigar_by_pov <- svytable(~binned_RATCAT+CIGARST_A,
                         design = nhis18_design)

#pipe use by poverty level
pipe_by_pov <- svytable(~binned_RATCAT +PIPEST_A,
                        design = nhis18_design)

#smokeless tobacco use by poverty level
smkles_by_pov <- svytable(~binned_RATCAT+SMOKELSST_A,
                          design = nhis18_design)
```

```{r}
cig_by_povDF <- df_function(cig_by_pov, binned_RATCAT, SMKCIGST_A)
cig_by_povDF$`Type of Smoke` <- ifelse(cig_by_povDF$`Type of Smoke` == "SMKCIGST_A", "Cigarette", "")

#
ecig_by_povDF <- df_function(ecig_by_pov, binned_RATCAT, SMKECIGST_A)
ecig_by_povDF$`Type of Smoke` <- ifelse(ecig_by_povDF$`Type of Smoke` == "SMKECIGST_A", "E-Cigarette", "")

#
cigar_by_povDF <- df_function(cigar_by_pov, binned_RATCAT, CIGARST_A)
cigar_by_povDF$`Type of Smoke` <- ifelse(cigar_by_povDF$`Type of Smoke` == "CIGARST_A", "Cigar", "")

#
pipe_by_povDF <- df_function(pipe_by_pov, binned_RATCAT, PIPEST_A)
pipe_by_povDF$`Type of Smoke` <- ifelse(pipe_by_povDF$`Type of Smoke` == "PIPEST_A", "Pipe", "")

#
smkles_by_povDF <- df_function(smkles_by_pov, binned_RATCAT, SMOKELSST_A)
smkles_by_povDF$`Type of Smoke` <- ifelse(smkles_by_povDF$`Type of Smoke` == "SMOKELSST_A", "Smokeless Tobacco", "")

smoking_by_pov <- rbind(cig_by_povDF, ecig_by_povDF, cigar_by_povDF, pipe_by_povDF,smkles_by_povDF)
kable(smoking_by_pov, caption ="Smoking Prevalence by Ratio of Family Income to Federal Poverty Level")

```
\newpage
### Smoking Prevalance by Sexual Orientation 

```{r}
cig_by_sexorient <- svytable(~ORIENT_A + SMKCIGST_A,
                   design = nhis18_design)

#e-cig use by poverty level
ecig_by_sexorient <- svytable(~ORIENT_A +SMKECIGST_A,
                        design = nhis18_design)

#cigar use by poverty level
cigar_by_sexorient <- svytable(~ORIENT_A+CIGARST_A,
                         design = nhis18_design)

#pipe use by poverty level
pipe_by_sexorient <- svytable(~ORIENT_A+PIPEST_A,
                        design = nhis18_design)

#smokeless tobacco use by poverty level
smkles_by_sexorient <- svytable(~ORIENT_A+SMOKELSST_A,
                          design =nhis18_design)
```


```{r}
cig_by_sexorientDF <- df_function(cig_by_sexorient, ORIENT_A, SMKCIGST_A)
cig_by_sexorientDF$`Type of Smoke` <- ifelse(cig_by_sexorientDF$`Type of Smoke` == "SMKCIGST_A", "Cigarette", "")

#
ecig_by_sexorientDF <- df_function(ecig_by_sexorient, ORIENT_A, SMKECIGST_A)
ecig_by_sexorientDF$`Type of Smoke` <- ifelse(ecig_by_sexorientDF$`Type of Smoke` == "SMKECIGST_A", "E-Cigarette", "")

#
cigar_by_sexorientDF <- df_function(cigar_by_sexorient, ORIENT_A, CIGARST_A)
cigar_by_sexorientDF$`Type of Smoke` <- ifelse(cigar_by_sexorientDF$`Type of Smoke` == "CIGARST_A", "Cigar", "")

#
pipe_by_sexorientDF <- df_function(pipe_by_sexorient, ORIENT_A, PIPEST_A)
pipe_by_sexorientDF$`Type of Smoke` <- ifelse(pipe_by_sexorientDF$`Type of Smoke` == "PIPEST_A", "Pipe", "")

#
smkles_by_sexorientDF <- df_function(smkles_by_sexorient, ORIENT_A, SMOKELSST_A)
smkles_by_sexorientDF$`Type of Smoke` <- ifelse(smkles_by_sexorientDF$`Type of Smoke` == "SMOKELSST_A", "Smokeless Tobacco", "")

smoking_by_sexorient <- rbind(cig_by_sexorientDF, ecig_by_sexorientDF, cigar_by_sexorientDF, pipe_by_sexorientDF,smkles_by_sexorientDF)
kable(smoking_by_sexorient, caption ="Smoking Prevalence by Sexual Orientation")

```

### Smoking Prevalence by Mental Health status

```{r}
mental_health_df_function <- function(object, col_name_1, col_name_2){
  object %>% 
  as.data.frame()%>%
  filter({{col_name_1}} == "Yes")%>%
  gather({{col_name_1}}, key = "Mental Health", value = "Mental_hlth_status")%>%
  gather({{col_name_2}}, key = "Type of Smoke", value = "Smoking Status")%>%
  spread(`Smoking Status`, Freq)
  
}



#creating depression data frames
cig_by_depress <- 
  svytable(~DEPEV_A + SMKCIGST_A,
                           design = nhis18_design)
cig_by_depressDF <- mental_health_df_function(cig_by_depress, DEPEV_A, SMKCIGST_A)


ecig_by_depress <- svytable(~DEPEV_A + SMKECIGST_A,
                           design = nhis18_design)
ecig_by_depressDF <- mental_health_df_function(ecig_by_depress, DEPEV_A, SMKECIGST_A)


cigar_by_depress <- svytable(~DEPEV_A + CIGARST_A,
                           design = nhis18_design)
cigar_by_depressDF <- mental_health_df_function(cigar_by_depress, DEPEV_A, CIGARST_A)


pipe_by_depress <- svytable(~DEPEV_A + PIPEST_A,
                           design = nhis18_design)
pipe_by_depressDF <- mental_health_df_function(pipe_by_depress, DEPEV_A, PIPEST_A)


smkles_by_depress <- svytable(~DEPEV_A + SMOKELSST_A,
                           design = nhis18_design)
smkles_by_depressDF <- mental_health_df_function(smkles_by_depress, DEPEV_A, SMOKELSST_A)


#creating anxiety data frames
cig_by_anxiety <- svytable(~ANXEV_A + SMKCIGST_A,
                           design = nhis18_design)
cig_by_anxietyDF <- mental_health_df_function(cig_by_anxiety, ANXEV_A, SMKCIGST_A)


ecig_by_anxiety <- svytable(~ANXEV_A + SMKECIGST_A,
                           design = nhis18_design)
ecig_by_anxietyDF <- mental_health_df_function(ecig_by_anxiety, ANXEV_A, SMKECIGST_A) 


cigar_by_anxiety <- svytable(~ANXEV_A + CIGARST_A,
                           design = nhis18_design)
cigar_by_anxietyDF <- mental_health_df_function(cigar_by_anxiety, ANXEV_A, CIGARST_A)


pipe_by_anxiety <- svytable(~ANXEV_A + PIPEST_A,
                           design = nhis18_design)
pipe_by_anxietyDF <- mental_health_df_function(pipe_by_anxiety, ANXEV_A, PIPEST_A)


smkles_by_anxiety <- svytable(~ANXEV_A + SMOKELSST_A,
                           design = nhis18_design)
smkles_by_anxietyDF <- mental_health_df_function(smkles_by_anxiety, ANXEV_A, SMOKELSST_A)


smoking_by_mentalhlth <- bind_rows(cig_by_depressDF, cig_by_anxietyDF, 
                                   ecig_by_depressDF, ecig_by_anxietyDF,
                                   pipe_by_depressDF, pipe_by_anxietyDF,
                                   cigar_by_depressDF, cigar_by_anxietyDF,
                                   smkles_by_depressDF, smkles_by_anxietyDF)


smoking_by_mentalhlth <- select(smoking_by_mentalhlth, -Mental_hlth_status)


smoking_by_mentalhlth$`Type of Smoke` <- ifelse(smoking_by_mentalhlth$`Type of Smoke` == "SMKCIGST_A", "Cigarette",
                                         ifelse(smoking_by_mentalhlth$`Type of Smoke` == "SMKECIGST_A", "E-cigarette",
                                         ifelse(smoking_by_mentalhlth$`Type of Smoke` == "PIPEST_A", "Pipe",
                                         ifelse(smoking_by_mentalhlth$`Type of Smoke` == "CIGARST_A", "Cigar",
                                         ifelse(smoking_by_mentalhlth$`Type of Smoke` == "SMOKELSST_A", "Smokeless Tobacco", "")))))

smoking_by_mentalhlth$`Mental Health` <- ifelse(smoking_by_mentalhlth$`Mental Health` == "DEPEV_A", "Depression",
                                         ifelse(smoking_by_mentalhlth$`Mental Health` == "ANXEV_A", "Anxiety", ""))

smoking_by_mentalhlth <- mutate(smoking_by_mentalhlth, `Prevalence (%)` = round((Yes/(Yes + No))*100, 1))
kable(smoking_by_mentalhlth, caption = "Prevalence of Smoking among people with Mental health Problems")
```
\newpage
## Dual Smoking Prevalence (Cigarette and other Products)

```{r}
cig_by_agedual <- svytable(~binned_age + SMKCIGST_A,
                   design = nhis18_design)
cig_by_agedual <- cig_by_agedual%>%
  as.data.frame()%>%
  spread(`SMKCIGST_A`, Freq)%>%
  mutate(`Prevalence of cigarette (%)` = round((Yes/(Yes + No))*100, 1))%>%
  select(binned_age, `Prevalence of cigarette (%)`)


ecig_by_agedual <- svytable(~binned_age + SMKECIGST_A,
                        design = nhis18_design)
ecig_by_agedual <- ecig_by_agedual%>%
  as.data.frame()%>%
  spread(`SMKECIGST_A`, Freq)%>%
  mutate(`Prevalence of E-cigarette (%)` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Prevalence of E-cigarette (%)`)
  


cigar_by_agedual <- svytable(~binned_age +CIGARST_A,
                         design = nhis18_design)
cigar_by_agedual <- cigar_by_agedual%>%
  as.data.frame()%>%
  spread(`CIGARST_A`, Freq)%>%
  mutate(`Prevalence of Cigar (%)` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Prevalence of Cigar (%)`)


pipe_by_agedual <- svytable(~binned_age + PIPEST_A,
                        design = nhis18_design)
pipe_by_agedual <- pipe_by_agedual%>%
  as.data.frame()%>%
  spread(`PIPEST_A`, Freq)%>%
  mutate(`Prevalence of Pipe (%)` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Prevalence of Pipe (%)`)
  

smkles_by_agedual <- svytable(~binned_age + SMOKELSST_A,
                          design =nhis18_design)
smkles_by_agedual <- smkles_by_agedual%>%
  as.data.frame()%>%
  spread(`SMOKELSST_A`, Freq)%>%
  mutate(`Prevalence of Smokeless Tobacco (%)` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Prevalence of Smokeless Tobacco (%)`)
  

cig_ecig_by_agedual <- svytable(~binned_age + cig_ecig,
                              design = nhis18_design)
cig_ecig_by_agedual <- cig_ecig_by_agedual%>%
   as.data.frame()%>%
  spread(cig_ecig, Freq)%>%
  mutate(`Dual prevalence cigaratte and e-cig (%)` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Dual prevalence cigaratte and e-cig (%)`)
  

cig_pipe_by_agedual <- svytable(~binned_age + cig_pipe,
                              design = nhis18_design)
cig_pipe_by_agedual <- cig_pipe_by_agedual%>%
  as.data.frame()%>%
  spread(`cig_pipe`, Freq)%>%
  mutate(`Dual prevalence cigaratte and pipe (%)` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Dual prevalence cigaratte and pipe (%)`)

cig_cigar_by_agedual <- svytable(~binned_age + cig_cigar,
                               design = nhis18_design)
cig_cigar_by_agedual <- cig_cigar_by_agedual%>%
  as.data.frame()%>%
  spread(`cig_cigar`, Freq)%>%
  mutate(`Dual prevalence cigaratte and cigar (%)` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Dual prevalence cigaratte and cigar (%)`)
  

cig_smkles_by_agedual <- svytable(~binned_age + cig_smkles,
                                design = nhis18_design)
cig_smkles_by_agedual <- cig_smkles_by_agedual%>%
  as.data.frame()%>%
  spread(`cig_smkles`, Freq)%>%
  mutate(`Dual prevalence cigaratte and smokeless tobacco (%)` = round((Yes/(Yes + No))*100, 1))%>%
  select(`Dual prevalence cigaratte and smokeless tobacco (%)`)
  
cig_ecig_table <- bind_cols(cig_by_agedual, ecig_by_agedual, cig_ecig_by_agedual)
kable(cig_ecig_table, caption = "Dual Prevalence of Cigarette and E-cigarette")

cig_cigar_table <- bind_cols(cig_by_agedual, cigar_by_agedual, cig_cigar_by_agedual)
kable(cig_cigar_table, caption = "Dual Prevalence of Cigarette and Cigar")

cig_pipe_table <- bind_cols(cig_by_agedual, pipe_by_agedual, cig_pipe_by_agedual)
kable(cig_pipe_table, caption = "Dual Prevalence of Cigarette and Pipe")

cig_smkles_table <- bind_cols(cig_by_agedual, smkles_by_agedual, cig_smkles_by_agedual)
kable(cig_smkles_table, caption = "Dual Prevalence of Cigarette and Smokeless Tobacco")
```